---
title: "Open data survey"
author: "Tomas Klingström"
date: '2022-05-11'
output:
  html_document:
    code_folding: hide
---

```{r setup_01, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# About this report
This report is designed with two purposes in mind. 

If read directly without opening the code chunks the report provides a comparative analysis of the State of Open Data survey 2021 published by Digital Science (https://doi.org/10.6084/m9.figshare.17081231) and a community specific survey to survey the State of Open Data and attitudes towards FAIR data policies conducted by the Pigweb consortium. The Pigweb study is built on the template provided by the State of Open Data Survey to maximise the comparability between the pig research community participating in Pigweb and the much larger study conducted by Digital Science and Springer Nature.

Opening the code chunks provided in the document or downloading the github repository (https://github.com/SGBC/survey) enables researchers to copy the report and reuse it as a template for their own comparative studies. The document is divided into a number of code chunks with data pruning and functions at the top followed by the report with the code chunks generating data interspersed between them.


```{r prep_01, echo=F, eval = F, message=FALSE, warning=FALSE}
# install packages
install.packages("knitr")
install.packages("lattice")
install.packages("tidyverse")
install.packages("likert")
install.packages("MASS")
install.packages("psych")
install.packages("viridis")
install.packages("ggplot2")
install.packages("here")
install.packages("devtools")
install.packages("rgr")
install.packages("readxl")
install.packages("ufs")
install.packages("writexl")

```


```{r prep_02, echo=F, eval = F, message=FALSE, warning=FALSE}
# set options
options(stringsAsFactors = F)         # no automatic data transformation
options("scipen" = 100, "digits" = 4) # suppress math annotation
# install packages
library(knitr)
library(lattice)
library(tidyverse)
library(likert)
library(MASS)
library(psych)
library(viridis)
library(ggplot2)
library(here)
library(devtools)
library(rgr)
library(readxl)
library(writexl)
```
```{r pruning_01, echo=T, eval = F, message=FALSE, warning=FALSE}

#pigw21 <- read_excel("pigw21.xlsx")
sod21 <- read_excel("sod21.xlsx", skip = 1)
pigw21s <- read_excel("pigw21s.xlsx")

#The below code chunks were used to ensure that data cannot be traced back to respondents. The data supplied with the github repository has already been treated with the below steps.

#In the pigweb survey the last question was for respondents to provide their e-mail address and organisation for follow up questions. This is personal information which is not to be shared outside the limited timesap of the project.
#pigw21 = pigw21[1:(length(pigw21)-6)]

#Apart from directly identifiable information it is important to ensure that combinations of information cannot be used to trace the respondents. In this case we have therefore decided to separate the respondent data from the rest of the survey and scramble the rows. Thereby combinations such as year of first publication and major source of finance cannot be used to identify respondents by a process of elimination.
#
#This snippet take the first 9 columns of the pigw21 dataset, put them in a separate dataframe and shuffles each column before putting it back together.
#pigrespondents = dplyr::select(pigw21, 1:9)
#pigw21 = dplyr::select(pigw21, !1:9)
#pigrespondents = as.data.frame(lapply(pigrespondents, sample))
#pigw21 = cbind(pigrespondents, pigw21)
#write_xlsx(pigw21, path = "pigw21s.xlsx")
#The shuffled file is the file shared in the supplementary data and loaded at the start of this chunk. 

```

## Data in the survey
The questionnaire contain over 200 different answers per respondent and can be broken down into 6 different categories, information about the respondent, questions about the respondents research data, questions about the respondents usage of data and finally views on credit and recognition of data. There is also a final section on information about the respondent which is not publicly shared as it would provide the means to identify the respondents of the survey. There are four types of questions used in the survey and shown in this report.

1. Likert scale questions, usually using done with a five point scale going from "I strongly disagree" to "I strongly agree". These are reported using an empirical cumulative distribution function with one graph each for the State of Open Data and Pigweb survey. Hypothesis testing with calculation of P-values are doing using the Kolmogorov-Smirnov test with the alternate hypothesis being that respondents are drawn from two populations with different preferences
2. Non-numeric single choice questions, selecting between different options the respondent select the most fitting one. A frequency bar plot with the different alternatives is used to visualize these responses.
3. Multiple choice questions, respondents may select multiple answers to the question.A frequency bar plot with the different alternatives is used to visualize these responses with the frequency being the number of respondents who selected an answer divided by the number of respondents.
.

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
