---
title: "Open data survey"
author: "Tomas Klingström"
date: '2022-05-11'
output:
  html_document:
    code_folding: hide
---

```{r setup_01, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# About this report
This report is designed with two purposes in mind. 

If read directly without opening the code chunks the report provides a comparative analysis of the State of Open Data survey 2021 published by Digital Science (https://doi.org/10.6084/m9.figshare.17081231) and a community specific survey to survey the State of Open Data and attitudes towards FAIR data policies conducted by the Pigweb consortium. The Pigweb study is built on the template provided by the State of Open Data Survey to maximise the comparability between the pig research community participating in Pigweb and the much larger study conducted by Digital Science and Springer Nature.

Opening the code chunks provided in the document or downloading the github repository (https://github.com/SGBC/survey) enables researchers to copy the report and reuse it as a template for their own comparative studies. The document is divided into a number of code chunks with data pruning and functions at the top followed by the report with the code chunks generating data interspersed between them.


```{r prep_01, echo=F, eval = F, message=FALSE, warning=FALSE}
# install packages
install.packages("knitr")
install.packages("lattice")
install.packages("tidyverse")
install.packages("likert")
install.packages("MASS")
install.packages("psych")
install.packages("viridis")
install.packages("ggplot2")
install.packages("here")
install.packages("devtools")
install.packages("rgr")
install.packages("readxl")
install.packages("ufs")
install.packages("writexl")

```


```{r prep_02, echo=F, eval = F, message=FALSE, warning=FALSE}
# set options
options(stringsAsFactors = F)         # no automatic data transformation
options("scipen" = 100, "digits" = 4) # suppress math annotation
# install packages
library(knitr)
library(lattice)
library(tidyverse)
library(likert)
library(MASS)
library(psych)
library(viridis)
library(ggplot2)
library(here)
library(devtools)
library(rgr)
library(readxl)
library(writexl)
```
```{r pruning_01, echo=T, eval = F, message=FALSE, warning=FALSE}

#pigw21 <- read_excel("pigw21.xlsx")
sod21 <- read_excel("sod21.xlsx", skip = 1)
pigw21s <- read_excel("pigw21s.xlsx")

#The below code chunks were used to ensure that data cannot be traced back to respondents. The data supplied with the github repository has already been treated with the below steps.

#In the pigweb survey the last question was for respondents to provide their e-mail address and organisation for follow up questions. This is personal information which is not to be shared outside the limited timesap of the project.
#pigw21 = pigw21[1:(length(pigw21)-6)]

#Apart from directly identifiable information it is important to ensure that combinations of information cannot be used to trace the respondents. In this case we have therefore decided to separate the respondent data from the rest of the survey and scramble the rows. Thereby combinations such as year of first publication and major source of finance cannot be used to identify respondents by a process of elimination.
#
#This snippet take the first 9 columns of the pigw21 dataset, put them in a separate dataframe and shuffles each column before putting it back together.
#pigrespondents = dplyr::select(pigw21, 1:9)
#pigw21 = dplyr::select(pigw21, !1:9)
#pigrespondents = as.data.frame(lapply(pigrespondents, sample))
#pigw21 = cbind(pigrespondents, pigw21)
#write_xlsx(pigw21, path = "pigw21s.xlsx")
#The shuffled file is the file shared in the supplementary data and loaded at the start of this chunk. 

sod21Done = dplyr::select(sod21, 1:9)
pigw21Done = dplyr::select(pigw21,1:4)
sod21 = dplyr::select(sod21, !1:9)
pigw21 = dplyr::select(pigw21,!1:4)

```

## Data in the survey
The questionnaire contain over 200 different answers per respondent and can be broken down into 6 different categories, information about the respondent, questions about the respondents research data, questions about the respondents usage of data and finally views on credit and recognition of data. There is also a final section on information about the respondent which is not publicly shared as it would provide the means to identify the respondents of the survey. There are three types of questions used in the survey and shown in this report.

1. Likert scale questions, usually with a five point scale going from "I strongly disagree" to "I strongly agree". These are reported using an empirical cumulative distribution function with one line each for the State of Open Data and the Pigweb survey. Hypothesis testing with calculation of P-values is done with a Kolmogorov-Smirnov test with the alternate hypothesis being that respondents are drawn from two populations with different preferences
2. Single choice questions, selecting between different options the respondent select the most fitting one. A frequency bar plot with the different alternatives is used to visualize these responses.
3. Multiple choice questions, respondents may select multiple answers to the question.A frequency bar plot with the different alternatives is used to visualize these responses with the frequency being the number of respondents who selected an answer divided by the number of respondents.
.

```{r functions_01, echo=F, eval = F, message=FALSE, warning=FALSE}
#The three types of functions to visualise data go here.

#In the block below these each question is analysed. 
#Note: Not all respondents answered all questions so frequencies need to have the actual number in the denominator.
#Several single choice and multipel choice questions got "other" as a response and then the following column is the free text response, listing these responses separately would be good. 

#An example file is in this folder.
```

The below section is an example of "the old approach" where each chunk would contain all the necessary code, the idea is to split the logic so that data cleaning from surveys is done in the chunk and Dataframes with sorted data are sent along with the question names to the function generating graphs.

```{r question_1, echo=T, eval = F, message=FALSE, warning=FALSE}
Example of data analysis
q121 = dplyr::select(sod21,10:18)

respondentsPig = dplyr::select(pigweb,5:7,10:14)
respondentsPig$source = 'pig'
outPutNames= c('When was the last occasion that you published or submitted a manuscript to a journal?', 'In which year was your first peer-reviewed research article published?', 'Which of the following best describes your primary area of interest?','Yes, within my institution','Yes, within my country','Yes internationally','No', 'I dont know')
colnames(respondentsSoD21) = c('Q1', 'Q2', 'Q3','Q4','Q5','Q6','Q7', 'Q8')
colnames(respondentsPig) = c('Q1', 'Q2', 'Q3','Q4','Q5','Q6','Q7', 'Q8')

# Question 1 'When was the last occasion that you published or submitted a manuscript to a journal?'
#This section use dplyr:recode to convert the State of Open Data survey to numbers so we can treated responses as a Likert scale.
#Values are the plotted from both surveys with GGplot and a two-sided Kolmogorov-Smirnov test is used to test the two-sided hypothesis that the
#samples come from the same dataset (ie null hypothesis is that the two datasets come from the same distribution). 

#unique(respondentsSoD21) #unique() is used to identify the unique answers of the question.
respondentsSoD21$Q1 = dplyr::recode(respondentsSoD21$Q1, "Within the last year" = 1, "1-2 years ago" = 2, "3-5 years ago" = 3, "More than 5 years ago" = 4, "I have never submitted a manuscript to a journal" = 5)
ggplot() +
     geom_step(aes(x = as.numeric(Q1)), data = respondentsSoD21, stat = "ecdf") + 
     geom_step(aes(x = as.numeric(Q1)), data = respondentsPig, stat = "ecdf", color="#c78b90") +
  scale_x_discrete("Time since most recent publication", limits = c("Within the last year", "1-2 years ago", "3-5 years ago", "More than five years ago"))

ks.test(respondentsSod21Pub$Q1, respondentsPig$Q1, ifresult = FALSE) #Kolmogorov-Smirnov test for Q1

```

